Fast Sorting on Modern Computers

### 2005-08-05 docs/tech_report/quick.tex
removed last unknown reference fixed grpahics

The pseudo-median-of-5 partitioning performs slightly better than the
median-of-3, and pseudo-median-of-7 performs slightly better again, in
terms of branch prediction. Figure \ref{TODO} shows the cycle count of each of
the quicksorts, showing that a pseudo-median-of-7 offers the greatest
trade-off between the reduced number of branches and instructions, and the
increase in branch mispredictions.

%TODO do we add more graphs here?

>>>>

The pseudo-median-of-5 partitioning performs slightly better than the
median-of-3, and pseudo-median-of-7 performs slightly better again, in
terms of branch prediction. Figure \ref{quick_median_cycles} shows the cycle
count of each of the quicksorts, showing that a median-of-3 offers the greatest
trade-off between the number of instructions and the increase in branch
mispredictions.

\begin{figure}
\includegraphics{plots/quick_median_cycles.eps}
\caption{Empiric cycles count for quicksort with varying medians}
\label{quick_median_cycles}
\end{figure}
